\section{Motivation}
This student report is written as part of a learning project. Therefore we must comply with the study regulation.
The study regulation states that the main focus of this semester's project is to gain knowledge of, and develop, Internet applications, -agents, or -services.
The goal is thus to create an Internet application that provides a service with focus on agent technologies, scalability and data intensity.

\subsection{Security Systems}
In their current form most security systems consist of a set of sensors and cameras, each covering a limited amount of space.
Both a sensor and a camera is limited by its range and spectrum.
As a consequence security systems require a large amount of hardware to monitor a large area to a satisfying degree.
%Hardware is expensive and therefore the cost of....
However such a surveillance system still suffer from most of its hardware components being static.
This means that if a sensor is triggered in an area not covered by a camera angle, a security company would have to send a guard to the location to investigate the source of the alarm.
The static nature of security systems combined with the high costs security guards makes it very expensive for a company to properly secure their property.\footnote{Sources for this section, pretty important}

A possible solution to the high cost and static nature of security systems could be a drone-based\footnote{What do we mean by a drone} surveillance system where cameras are placed on a drone capable of flight.
In such a system a guard would be able to access and control a drone through a web application to investigate what triggered an alarm, and based on a video stream determine whether or not to send someone to the location.
Moveable cameras would reduce the amount of hardware required, and the manpower required to investigate alarms.
Therefore the idea of a drone-based surveillance system is interesting to investigate.

The goal of this project is to develop a drone-based surveillance system, in order to reduce economical cost and save manpower.


%Old: static (Both in terms of camereas and possibly the controlcenter), expensive, slow in response (Regular alarm systems).

%New: dynamic, controllable from a single source, possibly cheaper