%*******************************************************
% Abstract
%*******************************************************
%\renewcommand{\abstractname}{Abstract}
\pdfbookmark[1]{Abstract}{Abstract}
\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Abstract}
Video surveillance is becoming more and more used around the world.
Governments use it to prevent criminal activities and terror, while the private sector use it to surveil their property and for gathering crime related evidence.
The ways technology allows us to video surveil today is, however, quite expensive and has its limitations such as the amount of needed hardware to get a sufficient degree of surveillance and the installation costs of this equipment. \\

This paper seeks to take advantage of modern technology to provide a new approach of video surveil large areas in a cost-efficient way. 
A proof of concept solution that uses unmanned air-crafts with mounted cameras -- drones -- and a web-interface for user interacting based on a scalable infrastructure is designed and implemented.
The goal is a scalable web-application that allows multiple users to control and view the video stream from such drones to do remote and cost-efficient surveillance of large areas. \\

The system that was developed in this student project is a proof of concept solution.
It also shows that if better hardware is available, a solution that uses drones to surveil large our-door areas is possible to deploy.

\endgroup			

\vfill