\section{Functionality distribution}
\label{sec:functionality_distribution}
% Hvilke funktionaliteter skal dækkes?
% Hvilke instancer dækker hvad?
% Hvorfor gør de det?

The functionality of the system can be derived from the acceptance tests.
This section will cover what instances are responsible for each functionality.

The need for storing data is derived from \at{1}, as previously described this is handled by the database \deno{DB}, which is a part of \deno{M}.
\at{2} sets the need for a dynamic response to \deno{B}, which requires processing of the stored data.
This processing is handled by Web or \deno{W} as the structure contains a singleton server solution.

Knowing that \deno{S} has a dynamic location relative to \deno{M}, this requires \deno{S} to send a signal to the daemon or \deno{D} in order for \deno{M} to get the location of \deno{S} on the network.
\deno{D} is then responsible for being able to receive incoming signals from \deno{S}.

Displaying video is required of \deno{B} by \at{3}.
The video displayed by \deno{B} is a stream, which requires that \deno{S} sends out a video stream.
In order to control a drone, commands have to be provided to the drone, as required by \at{3}.
\deno{S} is responsible for being able to receive commands and have the drone execute the given command.
\at{29} enforces security of the command handler.
\deno{S} is the only instance with a direct link to the drone, this makes \deno{S} responsible for the command handler's security.

% While Section~\ref{sec:application_structure} covered the overall structure of this application, this section will cover how the functionality is divided between the Master and the Slaves in the system. \\

% The Master is the users only way into the system.
% This access will always be via the users local web browser, where he sees the web system for \projectname{}.
% This web system and the database containing all informations about the system, drones, users etc. will be located on the Master.
% The Master is responsible for providing these services and coordinating the communication between the users and drones via the Slaves. \\

% A Slave is needed for every drone in the field, as the drones are not capable of long-distance communication.
% Therefore, in order to communicate with any drone, the communication must be channeled through its assigned Slave.
% This Slave is responsible for keeping contact with the drone and communicate directly with it via its API's.


